%        File: ThesisOutline.tex

%     Created: Tue Jun 21 01:00 AM 2022 E
% Last Change: Tue Jun 21 01:00 AM 2022 E
%
\documentclass[a4paper]{report}
\usepackage{outlines}
\usepackage{mathtools}
\begin{document}
\begin{titlepage}
    \title{Thesis Outline}
    \author{ Jeffrey Severino \\
        University of Toledo \\
        Toledo, OH  43606 \\
    email: jseveri@rockets.utoledo.edu}


    \maketitle

\end{titlepage}
\begin{abstract}
   Over the last 20 years, there has been an increase in computational fluid dynamic
   codes that have made numerical analysis more and more readily available, allowing
   turbomachine designers to create more novel designs. However, as airport noise 
   limitations become more restrictive over time, reducing aircraft takeoff and landing noise
   remains a prominent issue in the aviation community. One popular method to reduce
   aircraft noise is using acoustic liners placed on the walls of the engine inlet and
   exhaust ducts. These liners are designed to reduce the amplitude of acoustic modes
   emanating from the bypass fan as they propagate through the engine. The SWIRL
   code is a frequency-domain linearized Euler equation solver that is designed to predict
   the effect of acoustic liners on acoustic modes propagating in realistic sheared and
   swirling mean flows, guiding the design of more efficient liner configurations. 
   The purpose of this study is to validate SWIRL using the Method Of Manufactured Solutions
   (MMS). This study also investigated the effect of the integration and spatial 
   differencing methods on the convergence for a given Manufactured Solution. In addition, the
   effect of boundary condition implementation was tested. The improved MMS convergence 
   rates shown for these tests suggest that the revised SWIRL code provides
   more accurate solutions with less computational effort than the original formulation.
\end{abstract}
\begin{outline}[enumerate]
    \1 Introduction:
    \1[1-A.] Overview: Briefly explain why the study in being undertaken and what 
    main questions of foreshadowed problems will be addressed. Do this in a 
    general manner, because it will be done more specifically in the 
    following sections.
    This study is being conducted to make progress towards further understanding
    the numerical results for test cases that we do not have analytical solutions
    for.
    \1[1-B.] Statement of the Problem: Discuss the problem to be addressed in the
    research - the gaps, perplexities, or inadequacies in existing theory, 
    empirical knowledge, practice, or policy that prompted the study. The problem may be
    a theory that appears inadequate to explain known phenomena, the lack of 
    empirical data on a potentially interesting relationship between X and Y,
    or a common practice that appears ineffective. First state the problem
    generally, and then state the specifics that your research will address. In 
    quantitative research, the specifics will include the constructs studied.

    What is the research gap?

    The problem that researchers would want to see addressed in the researach:
    - ``What is missing'' or ``What is NOT ADDRESSED''
    - The question or problem that has not been answered in an area of specialization 
    - establishes the need or importance
    
    A turbomachine’s general flow condition includes a series of axial, tangential, and radial
    velocity components that vary depending on the location of concern. The swirling
    flow between fan stages has been an area of interest due to the potential for 
    acoustic treatment in a location previously avoided for its flow complexity, among other
    reasons. It is common in CAA codes to assume a uniform flow with superimposed
    wakes as a means of ``exciting'' certain acoustic modes within a duct. 
    This is different than SWIRL the user can provide an axial and tangential
    component as a function of radius which does not need to be uniform in either
    direction. 
    \1[1-C.] 
    The purpose of research is to acquire knowledge to address the problem or 
    certain aspects of it. Quantitative research tries to fulfill that purpose 
    by answering questions and/or testing hypotheses. Qualitative research 
    tries to fulfill that purpose by starting with foreshadowed problems,
    conjectures, or exploratory questions. Mixed-methods research may use both 
    approaches.
    The purpose of this study is to verify and validate SWIRL using the Method
    Of Manufactured solutions. The study will investigate the effect of the 
    integration and spatial differencing methods on the convergence for a series
    of Manufactured Solutions. Guidelines for setting unique \textit{auxillary} 
    conditions will be provided and its impact will be discussed. The use
    of fairing functions to set specific values at the boundaries will also be 
    provided. 
    \1[1-D.1] Research Questions or Hypotheses 
    Research questions address problems of the study. Each research question 
    seeks answers to a specific problem situation described in your study. 
    The type of the data and its availability determine the research quesitons.
    \textit{ For instance, research questions should relate to the conceptual 
    framework.} Each question should address and target a separate problem situation.

    A good hypothesis clearly states the expected relationship ( or difference) 
    between two variables and defines those variables in operational, measurable 
    terms. The hypothesis (or hypotheses) logically follows the review of related 
    literature and is based on the implications of previous research. A 
    well-developed hypothesis is testable, that is, can be confirmed or 
    dis-confirmed. 
    \1[1-D.2] Significance of the Study: Discuss the potential significance of
    the research. Significance comes from the uses that might be made of your
    results-how they might be of benefit to theory, knowledge, practice, policy,
    and future research. The potential significance should be based upon your
    literature revieW in Chapter 2. 
The significance of this study is that it will offer guidance when verifying a frequency
domain CAA code which has little liturature on. The goal is to couple code
verification and validation to the sound propagation in a duct problem and highlight
the issues that arise when using couple numerical techniques. The impact of 
the numerical scheme and number of grid points will be discussed/

    \1[1-E.] Conceptual Framework: Briefly summarize the theoreotical foundation 
    or conceptual framework(s) 
    \2 Research Questions:




    \1 Literature Review:
    \1[a]] The problem to be addressed and its significance
    \1[b]] The theoretical foundation or conceptual framework
    \1[c]] The research questions, hypotheses, foreshadowed problems, or conjectures
    \1[d]] The research paradigm and the methodology

    \2 Intro - Topics, Purposes, and Methods of the Literature Review.
    \3 Following the discovery of the acoustic impact of swirling flow in 
    1977, there has been a concerted effort to model sound propagation under
    such conditions (Cooper, A.J. and Peake N., Kousen, Posson ). 
    \2 Description and Critique of Scholarly Literature

    \3 Sound propagation in ducted flows can be modeled with the Linearized
    Euler Equations (LEE] though an initial value problem and normal mode analysis.
    The two normal mode analysis' have been studied by Golubev and Kousen where
    the flow is assumed to be isentropic, however Tam \& Auriault used a 
    non isentropic mean flow with constant density. For isentropic flows,
    the normal mode analysis requires the perturbation variables 
    to take the form of a linear equation. The components of the perturbation variables
    has been split into its mean and fluctuating parts in Kousen's study while
    Golubev , and Atassi splits the pertubation into a vortical and 
    potential part. This study will use Kousen's definition for the perturbation variables

    \4 While validation is apart of existing literature, there is currently
    no literature where the code verification technique of the method of 
    manufactured solutions (MMS) is used for the problem of sound propagation
    is a ducted flow. Although various code verification
    methods exist, the MMS is considered to be a gold-standard by experts 
    in computational modeling and simulation 
    (Oberkampf, W. L., and Roy, C. J., 2010. Verification and validation in scientific computing.)
    (Roache, P. J., 2009. Fundamentals of verification and validation). 
    The MMS provides a mathematical technique to verify that the LEE simulation 
    solves the equations correctly and that the spatial grid refinement 
    reduces the numerical error at an expected rate based on the numerical scheme used 
    (Roache, P. J., 2002. “Code verification by the method of manufactured solutions”. ) 

    \2 Inferences for Forthcoming study
    \3 The problem to be addressed in your research and its significance
    \4 The code verification presented in Maldando's work will be 
    improved by providing an observed order of accuracy
    \4 One key question that remains, is how well do unsteady linearized equations cap-
    ture the mechanisms of noise generation within realistic 
    turbomachinery flow? The numerical simulations for more complex 
    (axial shear + swirl) flows do not have analytical solutions and contain 
    different categories for the axial wavenumbers.  
    \3 possible research questions, hypotheses, foreshadowed problems, or 
    conjectures
    \4 What combination of spatial grid resolution and numerical scheme aid 
    the final result? The use of dissipation is apparent in literature, but the
    amount is not reported. 
    \4 Can the use of a desired damping rate help aid the sorting of axial wavenumbers
    \3 possible theoretical or conceptual framework to be used and
     possible research paradigms and methodologies used
    \4 MMS study 
    \4[-] Additional MMS framework will be explored (tanhSummation) and utilized
    to find MS' that meet the guidelines in Roaches work 
    \4[-] The use of MMS to test matrix construction for eigenvalue problem 
    \4 MES study
    \4[-] the analytical solution is known for uniform flow and is used for
    MES
   \4 Literature test case studies (some are shared with Maldonado)

    \begin{itemize}
        \item Kousen's Test Cases
            \subitem Cylinder, Uniform Flow with Liner (Table 4.3)
            \begin{align*}
                m &= 2 \\
                k &= \frac{\omega r_T}{A_T} = -1 \\
                M_x &= 0.5 \\
                \eta_T &= 0.72 + 0.42i\\
                \text{Confirm if 32 grid points is enough}
            \end{align*} 
            \subitem Cylinder, Shear Flow without Liner (Table 4.4)
            \begin{align*}
                m &= 0 \\
                kb &= \left(\frac{\omega r_T}{A_T}\right)b = 20 \\
                b &= r_{max} - r_{min} \\
                \tilde{r} = \frac{r}{b} \\
                M_x &= 0.3(1-\tilde{r})^{\frac{1}{7}} \\
                \eta_T &= 0\\
                \text{Confirm if 32 grid points is enough}
            \end{align*}
            \subitem Annulus, Shear Flow without Liner (Table 4.5)
            \begin{align*}
                m &= 0 \\
                kb &= \left(\frac{\omega r_T}{A_T}\right)b = 10 \\
                b &= r_{max} - r_{min}  = \frac{1}{7}\\
                k &= 70 \\
                \tilde{r} = \frac{r}{b} = 6.0 \\
                M_x &= 0.3\left(1 - 2 \left| \frac{r_{max}-r}{b} + 0.5 \right|  \right)^{\frac{1}{7}} \\
                \eta_T &= 0\\
                \text{Confirm if 32 grid points is enough}
            \end{align*}
            \subitem Annulus, Shear Flow with Liner (Table 4.6)
            \begin{align*}
                m &= 0 \\
                kb &= \left(\frac{\omega r_T}{A_T}\right)b = 10 \\
                b &= r_{max} - r_{min}  = \frac{1}{3}\\
                k &= 30 \\
                \tilde{r} = \frac{r}{b} = 2.0 \\
                M_x &= 0.3\left(1 - 2 \left| \frac{r_{max}-r}{b} + 0.5 \right|  \right)^{\frac{1}{7}} \\
                \eta_T &= 0.3 + 0.1i\\
                \text{Confirm if 32 grid points is enough}
            \end{align*}
    \end{itemize}

    \4[-] Kousen's test cases which were compared to P.N. Shankar's work and 
    then expanded for cases where data is needed . Maldonado has compared the same
    tests

    \2 Theoretical/Conceptual Framework for Forthcoming Study (May appear in 
    methods chapter)

    \1 Research Methodology
    \2 Conjectures, or Exploratory Questions:
    \2[-] What is the observed order of accuracy for SWIRL's second order and 
    fourth order solutions (MMS/MES)? How does the number of grid points 
    and manufactured solution effect the solution accuracy.  
    \2 Research Procedures - Describe in detail how the inquiry was undertaken.
    Generally the description should be thorough enough that other skilled
    researchers could approximately replicate your study from the description.
    \3 Introduce the epistemology that will guide the inquiry/
    Indicate the methodology used and why it was selected.
    \4 Aerodynamic Theoretical Background:
    The steady and unsteady aerodynamic models are presented here.
    \4 The MMS and tanh summation method will be used to define a sufficient test 
    case for the second/fourth order differencing schemes for the radial derivatives
    and for the approximated speed of sound obtained through numerical integration. To account 
    for acoustic liners as boundary conditons, fairing functions were used
    to impose boundary values for the radial velocity perturbation and for the 
    radial derivative of pressure.
    \3 Explain the theoretical perspective that will drive the research, and why it was selected. 
    \4 The need for a code verification study prompted the use of MMS and MES to
    investigate if SWIRL was coded correctly. In addition, the findings from these 
    studies inform the user how the numerical scheme is effecting the final solution which
    will offer insight for the more complicated flows.
    \3 Indicate the specific methods used and the justification for them. How were sites, cases, and
    informants selected? Why? What access did you unsuccessfully seek? Which people perhaps tried to
    minimize contact with you and which repeatedly sought it out? How did you collect your data? Why?
    The manufactured solutions were chosen such in a way that allows testing 
    for each term in SWIRL. Setting up the manufactured solutions this way 
    ensures that there is no variable unused.   
    \3 Indicate how you analyzed and interpreted your data, making sure the analysis was consistent with
    the selected methodology. If you inferred themes, explain how. If you coded the transcripts, explain
    the coding system and checks for coding reliability and validity. How did you analyze the data from
    the coding? How did you triangulate or otherwise verify findings? How did you interpret the full set
    of data?

    The 
    \1 Results of the Study
    \2 statement of the received results and their analysis
    \3 Results for MMS/MES/set of test cases will be presented. The MMS and MES
    will have errors and convergence rates associated with the schemes that are
    available in SWIRL.
    \2 Comparison of the obtained results and the initial goals/questions
    \1 Summmary
    \2 Discussion of the research results;
    \3 Discuss the convergence rates and make the case for fourth order schemes.
    \3 Discuss the effect on axial wavenumber categorization. 
    \2 Comparison of the obtained results with the findings of prior researchers
    \3 Discuss the appearance of nearly convected wavenumbers as the tests get more complex.
    \2 Suggestions regarding the use of the obtained findings for the further
    development of the topic and future investigation 
    \3 The use of GCI could give a grid which is closer to convergence
    \3 Limitations of the eigensolver
    \3 The use of a desired damping rate can be correlated to the length of a 
    Nacelle
    \3 Comparison against experimental data
    \1 Appendices
\end{outline}
\end{document}

