
%        File: WeeklyResearchReport_4_19_21.tex
%     Created: Mon Apr 19 08:00 AM 2021 E
% Last Change: Mon Apr 19 08:00 AM 2021 E
%
\documentclass[a4paper]{article}
\begin{document}
\begin{titlepage}

    \title{
    Daily Research Report}

    \author{ Jeffrey Severino \\
        University of Toledo \\
        Toledo, OH  43606 \\
    email: jseveri@rockets.utoledo.edu}


    \maketitle

\end{titlepage}
\section{Current Research Direction}
The current goal is to put the MMS to a closing. My idea is to do a particular
writeup for the MMS alone. I believe I have enough here for at least a first 
draft conference paper. By limiting the scope of this document to MMS alone, 
it will help me focus on getting a complete chapter for my thesis. 

\section{Research Performed}
I recently revisited my MMS and it was not so easy to dust off. I have 
been reminding myself what I did so I can reuse it again. The basic work flow is 
this:

\begin{enumerate}
    \item Using python, read the inputs that are in the main.f90 code. Variables 
        like radius, liner information, and frequency of concern is read in here
    \item Python symbolically defines the manufactured solutions for the 
        speed of sound and for the linearized euler equations
    \item Python generates FORTRAN code that defines the manufactured solution.
       \item Optional: Plot output before sent to FORTRAN.
\end{enumerate}

\section{Issues and Concerns}
I have very crude tests I made for my Python codes using pytest but never solidified 
them. I would like to conduct a code review of my work at the end of this week 
if possible.
\section{Planned Research}
Go back into my commit history right before I deviated from the MMS study.
\end{document}


