
%        File: WeeklyResearchReport_4_19_21.tex
%     Created: Mon Apr 19 08:00 AM 2021 E
% Last Change: Mon Apr 19 08:00 AM 2021 E
%
\documentclass[a4paper]{article}
\begin{document}
\begin{titlepage}

    \title{
    Daily Research Report}

    \author{ Jeffrey Severino \\
        University of Toledo \\
        Toledo, OH  43606 \\
    email: jseveri@rockets.utoledo.edu}


    \maketitle

\end{titlepage}
\section{Current Research Direction}
Write methods section of my the Method of Manufactured Solution for my thesis

\section{Research Performed}
Attended online lecture on scientific writing,

Notes from lecture

Importance of methods section:
\begin{itemize}
    \item Explains how the hypothesis is tested
    \item how the data is collected and analyzed.
    \item the methods section is important because it convinces the reader 
        that the study and results are believable. If the reader doubts your 
        findings they will look at the methods section. Methods will also help people
        trying to replicate the work if they get different answers.  
\end{itemize}

Content of the method section. An example research paper about apples was used

The question that is being asked is:

How does the color of sliced apple change over time, after being dipped in different 
chemicals?

The independent variable : chemical used on the apple. dependent variable 
change: color of apples.  other variables that could effect the results are discussed 
in the method

Organization:

\begin{enumerate}
    \item Object of Study 
        \subitem Explain what you are studying . The object of the study is NOT
        all the things used in your experiment/simulation 
    \item Treatment for the object 
        \subitem Explain what are you doing to your object/
        This is the independent variable: what are you going to change in between
        conditions.
    \item Procedure to collect the data 
        \subitem Explain what was measured and how it was measured 
        This is the dependent variable. The experiment is testing how this 
        changes based on the independent variable.
    \item Procedure to analyze data
        \subitem Transform the data.
        \subitem Formula, software, statistical analysis.  
\end{enumerate}

Draft of methods 

\begin{enumerate}
    \item Object of Study
        \subitem The method of manufactured solutions(MMS) is a code verification 
        procedure that is used to provide an analytical solution for SWIRl, a
        frequency domain, linearized euler equation code, for cases 
        that do not have a known analytical solution. The MMS is used to 
        obtain an order of accuracy for a given numerical approximation which 
        gives a measure of ``goodness'' for a given number of grid points.  
    \item Treatment for the object
        \subitem The number of grid points used for a given domain is often not 
        reported and is often different depending on the accuracy of the answer. In
        addition, many numerical codes rely on various numerical techniques, not just one, which can
        lead to a compounding of numerical error from an insufficient number 
        of grid points for a given numerical techique. Since the order of 
        accuracy is directly dependent on the numerical method 
        and number of grid points used, this study aims to outline a procedure
        for determining the minimum number of grid points need for a series of numerical techniques used 
        to obtain integrals and derivative approximations. 
    \item Procedure to collect the data 
        \subitem SWIRL uses a series of numerical techniques in a given run. MMS will
        be used to obtain a manufactured analytical solution and an order of accuracy for 
        the numerical integration used to compute the speed of sound. The MMS will 
        also be used for the radial derivatives within the linearized euler equations. A minimum
        number of 7 gridpoints will be used as a starting grid and the number
        of grid points will be doubled until the computed order of accuracy has reached 
        the expected order of accuracy for the given numerical scheme.  
    \item Procedure to analyze the data.
    \subitem To obtain a manufactured analytical solution a test function is chosen
        for each variable that is going to be approximated. Python's SciPy library
        was used to evaluate the expressions needed for the manufactured solution.
        A range of boundary conditions and auxillary conditons were used to make 
        the manufactured solution sufficient for computing an order of accuracy.
        The manufactured solutions were then converted to FORTRAN 90 to keep the 
        computation uniform with SWIRL.  
\end{enumerate}

 
\section{Issues and Concerns}
\begin{itemize}
    \item 7 grid points is too small, and it was suggested at the SIAM conference
        that I should play Around with the grid spacing because doubling the 
        grid points would be considerably slow. Right now it is at 8 iterations 
        for second order and the given test I chose.
\end{itemize}
\section{Planned Research}
This outline sort of serves as an introduction.  The results and discussion will
be after 

\end{document}


