\documentclass[a4paper]{article}
\usepackage{mathtools}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{pgfplots}
\usepackage{adjustbox}
\usepackage{booktabs}
\makeatletter
\let\latex@xfloat=\@xfloat
\def\@xfloat #1[#2]{%
    \latex@xfloat #1[#2]%
    \def\baselinestretch{1}
    \@normalsize\normalsize
    \normalsize
}
\makeatother
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{epigraph}
\usepackage{cancel}
\usepackage{xcolor}
\newcommand\Ccancel[2][black]{\renewcommand\CancelColor{\color{#1}}\cancel{#2}}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{pgfplots}
\usepackage{tabularx}
\DeclareUnicodeCharacter{2212}{−}
\usepgfplotslibrary{groupplots,dateplot}
\usetikzlibrary{patterns,shapes.arrows}
\pgfplotsset{compat=newest}
\begin{document}
\begin{titlepage}

    \title{
    Update Report}


    \author{ Jeffrey Severino \\
        University of Toledo \\
        Toledo, OH  43606 \\
    email: jseveri@rockets.utoledo.edu}


    \maketitle

\end{titlepage}
\section{Current Research Direction}
Thesis revision is currently in progress. The  ``Chapter 3: Theoretical Framework and Methods``
section  is nearly complete. It is missing the 
complete derivation for the wave equation at the start of the ''Analytical 
Solution to Sound Propagation in ducted flows``
but has the governing equations, the nonuniformities in swirling mean flow, the linearization
and the non dimensionalization that will be used.


\section{Research Performed}
The current Methods section is included. The initial results for the MMS
study is also included.  The goal is finalize what I can now and include my initial 
findings for the uniform flow case that contained the boundary problems.

%Here is the opening section for the third chapter,
%\input{Chapter-3-Theory-Aerodynamic-Models/aerodynamic_model}
%\input{Chapter-3-Theory-Aerodynamic-Models/aerodynamic_model_special_cases}
%
\section{Issues and Concerns}
Formatting is happening in parallel. There are missing labels and equation numbers
and some equations are not being referenced when mentioned, leading to confusion 
for the reader
\section{Planned Research}

\begin{itemize}
    \item Include the derivation for the wave equation that is used for validation
        work. I would like to start the ``Analytical Solution to Sound Propagation in 
        ducted flows'' section with this and emphasize that the equations outlined 
        above this section present the  eigenvalue problem, but the problem 
        can also be solved by solving a second order ODE for pressure, but this 
        has pros and cons that need to also be discussed.  
    \item The MMS theoretical background needs to also be included in its own 
        section prior the numerical methods section
\end{itemize}
\end{document}


