%        File: ManufacturedFlowFunctionsDocumentation.tex
%     Created: Wed Oct 13 01:00 PM 2021 E
% Last Change: Wed Oct 13 01:00 PM 2021 E
%
\documentclass[a4paper]{article}
\usepackage{mathtools}
\begin{document}
\section{Defining Manufactured Mean Flow Functions}

For SWIRL, the absolute bare minimum requirement is to define the corresponding
flow components for the domain of interest. SWIRL assumes no flow in the radial 
direction, leaving only two other components, axial and tangential for a 3D 
cylindrical domain. Since SWIRL is also non dimensionalized, the mean flow 
components are defined using the Mach number. SWIRL uses the tangential mach number
to obtain the speed of sound using numerical integration. The speed of sound
is then used to find the rest of the primative variables for the given flow. 

The goal is to manufacture functions that will test the numerical integration used 
to obtain the speed of sound. 
This requires a manufactured function for either
the tangential Mach number or the speed of sound. For example
\subsection{Checking if guidelines for creating manufactured solutions are followed}

\begin{enumerate}
    \item smooth
    \item general enough to exercise each term in the governing equations
    \item Enough derivatives to appropriately test scheme
    \item bounded by a small constant
    \item Make the same assumptions as code (non-dimensional variables, so they
        should not exceed one or be negative)
    \item Defined on a connected subset oF 2d/3d space
    \item function needs to make sense to the derivatives in the pde
\end{enumerate}

\subsection{Mean Flow (steady)}

Find: A manufactured solution that meets these guidelines. This work is exploring
how a function can be bounded  in other ways\ldots

(look at the tanh method paper)
\subsubsection{A tanh method for manufactured solutions}

Suppose there are two ``kinks'' , (write notes in planner in here)
\[ 1 = R + L \]

\begin{align*}
    \widetilde{A}(\widetilde{r}) &= 
    \sum_{j=1}^{n} R_{ij} +
    \sum_{j=1}^{n} L_{jn} + 
    S_{vertical} 
\end{align*}

where,

\begin{align*}
    R_{ij} = A \tanh \left( B \left( \widetilde{r}_i - \widetilde{r}_{j} \right) \right)\\
    L_{jn} = A \tanh \left( B \left( \widetilde{r}_j - \widetilde{r}_{n} \right) \right)\\
\end{align*}

$\widetilde{r}_i$ is the radial location, and $\widetilde{r}_j$ is the horizontal location of the kinks inflection point,
$r_n$ is the horizontal location of the last kink
\subsubsection{Speed of Sound}

\section{appendix}
Non-dimensionalize radius,
\begin{align}
    \widetilde{r}     &= \frac{r}{r_{max}}                \\
    \widetilde{r}_{min}   &= \frac{r_{min}}{r_{max}}    \\
    \widetilde{r}_{max}   &= \frac{r_{max}}{r_{max}} = 1
    \label{eq:1}
\end{align}
Define a new radial term, $\hat{r}$ to scale the radius to 0 to 1,
\begin{align}
    \hat{r} = 
    \frac{\widetilde{r}      - \widetilde{r}_{min}} 
         {\widetilde{r}_{max} - \widetilde{r}_{min}} \\
         \hat{r}_{max} &= 
         \frac{\widetilde{r}_{max}      - \widetilde{r}_{min}} 
         {\widetilde{r}_{max} - \widetilde{r}_{min}} = 1 \\
         \hat{r}_{min}
         \frac{\widetilde{r}_{min}      - \widetilde{r}_{min}} 
         {\widetilde{r}_{max} - \widetilde{r}_{min}} = 0 \\
    \label{eq:2}
\end{align}

The next step is to define the workflow for defining the manufactured solution 
for SWIRL
\end{document}
